Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
polishing false positives explanation; adding fixes for igor

The sources of false positives found in this experiment are as
follows: \textbf{Undefined Behavior.} False positives of this kind are
manifested when tests cover implementation-dependent behavior, as
defined in the ECMA262 specification~\cite{ecmas262-spec}. For
example, one of the tests from \jerry\ uses the function
\CodeIn{Number.toPrecision([precision])}, which translates a number to
a string, considering a given number of significant digits. The
floating-point approximation of the real value is
implementation-dependent, making the test to pass only in \chakra\ for
that test. As another example, some tests from \Fix{Y} use the
implementation-dependent description message\Mar{what is the name of
  the property?} encapsulated in an \CodeIn{Error} object in
assertions. As such, those tests fail in all engines but
\Fix{Y}. \textbf{Timeout/OME\footnote{ome is for out of memory
    error.}.} False positives of this kind manifest because the engine
that runs the test does not optimize the code as the original engine
and that has an effect in the test outcome.  The test may fail to
finish at the specified time budget or it exceeds the memory
budget. For example, a test case from the \jsc{} suite defines a
function with a tail-call recursion. The test fails in all engines but
\jsc{}, which implements tail-call optimization, which enables the
test to finish execution fast. \textbf{Not implemented.} False
positives of this kind manifest when a test fails because it covers a
function that is part of the official spec, but is not implemented in
the target engine yet. For example, at the time of writing, \chakra{}
does not implement by default various properties from the
\mcodeid{Symbol} object. These properties are only available
activating the ES6 experimental mode with the flag
\CodeIn{-ES6Experimental}. \Mar{pela explicacao de
  ``compile-in-all'', isto nao faz sentido.$\rightarrow$} \textbf{Non-Standanrd Element.} This kind
corresponds to the cases the test case relies on some non-standard
function or property of a standard object. \Mar{revise this.$\rightarrow$}\textbf{Unknown.} This
category includes the cases we were unable to confidently diagnose the
failure but we suspected it was a false alarm.

@@

>>>>

%%  As another example, some tests from \Fix{Y} use the
%% implementation-dependent description message\Mar{what is the name of
%%   the property?} encapsulated in an \CodeIn{Error} object in
%% assertions. As such, those tests fail in all engines but
%% \Fix{Y}.

The sources of false positives found in this experiment are as
follows: \textbf{Undefined Behavior.} False positives of this kind are
manifested when tests cover implementation-dependent behavior, as
defined in the ECMA262 specification~\cite{ecmas262-spec}. For
example, one of the tests from \jerry\ uses the function
\CodeIn{Number.toPrecision([precision])}, which translates a number to
a string, considering a given number of significant digits. The
floating-point approximation of the real value is
implementation-dependent, making that test to pass only in
\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
    error.}.} False positives of this kind typically manifest when the
engine that runs the test does not optimize the code as the original
engine of the test. As result, the test fails to finish at the
specified time budget or it exceeds the memory budget. For example, a
test case from \jsc{} defines a function with a tail-call
recursion. The test fails in all engines but \jsc{}, which implements
tail-call optimization. \textbf{Not implemented.} False positives of
this kind manifest when a test fails because it covers a function that
is part of the official spec, but is not implemented in the target
engine yet. For example, at the time of writing, \chakra{} does not
implement by default various properties from the \mcodeid{Symbol}
object. These properties are only available activating the ES6
experimental mode with the flag \CodeIn{-ES6Experimental}. \Mar{igor,
  nao consigo entender o porque deste caso nao dar aqueles erros
  (ReferenceError/TypeError) que vc. me mostrou e estourar na
  assercao. explique e de um exemplo concreto, por favor$\rightarrow$}
\textbf{Non-Standard Element.} This kind corresponds to the cases the
test case relies on some non-standard function or property of a
standard object. \Mar{igor, ha alguma explicacao/intuicao para
  explicar porque nao conseguir classificar
  isto?.$\rightarrow$}\textbf{Unknown.} This category includes the
cases we were unable to confidently diagnose the failure but we
suspected it was a false alarm.

@@

\Mar{----------------------------- estou aqui $\rightarrow$}
